Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-12 ms.tex
Add text about factoring likelihood

>>>>

\section{Method}

If we assume that the time and amplitude estimation errors are uncorrelated, then we can separate the likelihood into one factor that depends only on time and one that depends only on amplitude:
%
\begin{eqnarray*}
    \mathcal{L}(
        \hat{\tau}_1, \hat{\tau}_2, &\dots, \hat{\tau}_N,
        \hat{\rho}_1, \hat{\rho}_2, \dots, \hat{\rho}_N;
        \mathbf{n}, t_\oplus, D_\mathrm{L}, \iota, \psi, \phi_c) \\
    &= \mathcal{L}_\mathrm{TOA}(
        \hat{\tau}_1, \hat{\tau}_2, \dots, \hat{\tau}_N; \mathbf{n}, t_\oplus) \\
        &\times
        \mathcal{L}_\mathrm{SNR}(\hat{\rho}_1, \hat{\rho}_2, \dots, \hat{\rho}_N;
         \mathbf{n}, D_\mathrm{L}, \iota, \psi, \phi_c
    ).
\end{eqnarray*}
%
The \ac{TOA}-only factor depends only on the \ac{TOA} estimates $\hat{\tau}_1, \hat{\tau}_2, \dots, \hat{\tau}_N$, the unknown sky location $\mathbf{n}$ (or equivalently, the right ascension $\alpha$, declination $\delta$, and sidereal time), and the absolute \ac{TOA} at an arbitrary reference point (herein, the geocenter), $t_\oplus$.
%
\begin{equation}
    \mathcal{L}_\mathrm{TOA} \propto \exp \left[
        -\frac{1}{2} \sum_{i=1}^N \frac{\left(\hat{\tau}_i + \mathbf{n} \cdot \mathbf{r}_i / c - t_\oplus \right)^2}{\left(\hat{\rho_i} / \omega_{\mathrm{rms},i}\right)^2}
    \right]
\end{equation}
%
The \ac{SNR}-only factor depends only on the \ac{SNR} estimates $\hat{\rho}_1, \hat{\rho}_2, \dots, \hat{\rho}_N$, but it depends on the unknown sky location, luminosity distance $D_\mathrm{L}$, inclination $\mathrm{\iota}$, polarization angle $\psi$, and coalescence phase $\phi_c$.
%
\begin{equation}
    \mathcal{L}_\mathrm{SNR} \propto \exp \left[
        -\frac{1}{2} \sum_{i=1}^N \left(\hat{\rho}_i - \rho_i(\mathbf{n}, D_\mathrm{L}, \iota, \psi, \phi_c) \right)^2
    \right]
\end{equation}
